gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
in progress

```{r, echo=TRUE}
tbl_summary_2 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(
    by = trt,
    label = age ~ "Patient Age",
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = list(age ~ 2, 
                  all_categorical() ~ c(0, 0, 1)),
    missing = "no"
  )
```

>>>>

```{r, echo=TRUE}
tbl_summary_2 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(
    by = trt,
    type = all_continuous() ~ "continuous2",
    label = age ~ "Patient Age",
    statistic = list(all_continuous() ~ c("{N_nonmiss}", 
                                          "{mean} ({sd})", 
                                          "{median} ({p25}, {p75})", 
                                          "{min}, {max}"),
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = all_categorical() ~ c(0, 0, 1),
    missing = "no"
  )
```
